### 2019-11-06 README.Rmd
commit

# Use ggmatplot
ggmatplot(X,cbind(Y,Z), shape = c(16,1),legend_label =  c("X^2","X^2-2*X"),legend_title = "")
```

@@

# Modify legend label and axis
ggmatplot(iris_sub[,c(1,3)], iris_sub[,c(2,4)], shape = c("s","S"), legend_label =  c("Sepal","Petal"), legend_title = "", xlab = "Length", ylab="Width")
```

>>>>

# Use ggmatplot
ggmatplot(X,cbind(Y,Z), shape = c(16,1),legend_label =  c("X^2","X^2-2*X"),geom=c("point","line"))
```

@@

# Modify legend label and axis
ggmatplot(iris_sub[,c(1,3)], iris_sub[,c(2,4)], color = 1 ,shape = c("S","P"), xlab = "Length", ylab="Width")
```
